---
title: "Assignment 6"
author: "Jiahao Chen"
date: "11/19/2021"
output:
  word_document: default
  html_document: default
---


## 1
```{r}
library(lpSolveAPI)
lpec1<-make.lp(0,12)
set.objfn(lpec1,c(5,3,2,3,4,4,1,6,2,7,4,5))
lp.control(lpec1,sense='max')
```

```{r}
add.constraint(lpec1,c(1,1,0,0,0,0,0,0,0,0,0,0),"=",1)
add.constraint(lpec1,c(1,0,-1,0,-1,0,0,0,0,0,0,0),"=",0)
add.constraint(lpec1,c(0,1,0,-1,0,0,0,0,0,0,0,0),"=",0)
add.constraint(lpec1,c(0,0,0,0,1,-1,-1,0,0,0,0,0),"=",0)
add.constraint(lpec1,c(0,0,1,1,0,0,0,-1,-1,0,0,0),"=",0)
add.constraint(lpec1,c(0,0,0,0,0,0,1,0,0,0,0,-1),"=",0)
add.constraint(lpec1,c(0,0,0,0,0,1,0,1,0,0,-1,0),"=",0)
add.constraint(lpec1,c(0,0,0,0,0,0,0,0,1,-1,0,0),"=",0)
add.constraint(lpec1,c(0,0,0,0,0,0,0,0,0,1,1,1),"=",1)
Colnames<-c("X12","X13","X25","X35","X24","X47","X46","X57","X58","X89","X79","X69")
Rownames<-c("U1","U2","U3","U4","U5","U6","U7","U8","U9")
dimnames(lpec1)<-list(Rownames,Colnames)
write.lp(lpec1,filename = "Assignment6.lp",type = "lp")
solve(lpec1)
get.objective(lpec1)
```


```{r}
cbind(Colnames,get.variables(lpec1))
```

Running the LP formulation on any LP solver, the critical path is:

From node 1 to 2

From node 2 to 4

From node 4 to 7

From node 7 to 9

The duration of project is 17 times.




## 2 

```{r}
lpec2<-make.lp(0,8)
set.objfn(lpec2,c(4,6.5,5.9,5.4,5.15,10,8.4,6.25))
lp.control(lpec2,sense='max')
```

```{r}
add.constraint(lpec2,c(40,50,80,0,0,0,0,0),"<=",1000)
add.constraint(lpec2,c(0,0,0,60,45,60,0,0),"<=",1000)
add.constraint(lpec2,c(0,0,0,0,0,0,30,25),"<=",1000)
add.constraint(lpec2,c(40,0,0,0,0,0,0,0),">=",100)
add.constraint(lpec2,c(0,50,0,0,0,0,0,0),">=",100)
add.constraint(lpec2,c(0,0,80,0,0,0,0,0),">=",100)
add.constraint(lpec2,c(0,0,0,60,0,0,0,0),">=",100)
add.constraint(lpec2,c(0,0,0,0,45,0,0,0),">=",100)
add.constraint(lpec2,c(0,0,0,0,0,60,0,0),">=",100)
add.constraint(lpec2,c(0,0,0,0,0,0,30,0),">=",100)
add.constraint(lpec2,c(0,0,0,0,0,0,0,25),">=",100)
add.constraint(lpec2,c(40,50,80,60,40,60,30,25),"<=",2500)
set.type(lpec2,1:8,"integer")
Colnames<-c("S1","S2","S3","H1","H2","H3","C1","C2")
Rownames<-c("U1","U2","U3","U4","U5","U6","U7","U8","U9","U10","U11","U12")
dimnames(lpec2)<-list(Rownames,Colnames)
```


```{r}
write.lp(lpec2,filename = "Assignment6(2).lp",type = "lp")
```





```{r}
solve(lpec2)
get.objective(lpec2)
get.variables(lpec2)
```
```{r}
cbind(Colnames,get.variables(lpec2))
```
The ammout of stock shares(in thousand):

 "S1"     3 
 "S2"     5
 "S3"     2 
 "H1"     2 
 "H2"     3
 "H3"     12
 "C1"     30
 "C2"     4
 
The max return is $479,550.

The amount of dolloar invested in each stock(in thousand):

 "S1"     120
 "S2"     250
 "S3"     160 
 "H1"     120 
 "H2"     135
 "H3"     720
 "C1"     900
 "C2"     100
 
 
 
 
```{r}
#  no integer restriction
lpec3<-make.lp(0,8)
set.objfn(lpec3,c(4,6.5,5.9,5.4,5.15,10,8.4,6.25))
lp.control(lpec3,sense='max')
add.constraint(lpec3,c(40,50,80,0,0,0,0,0),"<=",1000000)
add.constraint(lpec3,c(0,0,0,60,45,60,0,0),"<=",1000000)
add.constraint(lpec3,c(0,0,0,0,0,0,30,25),"<=",1000000)
add.constraint(lpec3,c(40,0,0,0,0,0,0,0),">=",100000)
add.constraint(lpec3,c(0,50,0,0,0,0,0,0),">=",100000)
add.constraint(lpec3,c(0,0,80,0,0,0,0,0),">=",100000)
add.constraint(lpec3,c(0,0,0,60,0,0,0,0),">=",100000)
add.constraint(lpec3,c(0,0,0,0,45,0,0,0),">=",100000)
add.constraint(lpec3,c(0,0,0,0,0,60,0,0),">=",100000)
add.constraint(lpec3,c(0,0,0,0,0,0,30,0),">=",100000)
add.constraint(lpec3,c(0,0,0,0,0,0,0,25),">=",100000)
add.constraint(lpec3,c(40,50,80,60,40,60,30,25),"<=",2500000)
set.type(lpec3,1:8,"integer")
Colnames<-c("S1","S2","S3","H1","H2","H3","C1","C2")
Rownames<-c("U1","U2","U3","U4","U5","U6","U7","U8","U9","U10","U11","U12")
dimnames(lpec3)<-list(Rownames,Colnames)
```
 
```{r}
solve(lpec3)
get.objective(lpec3)
get.variables(lpec3)
```
 
```{r}
(log(get.objective(lpec3))-log(get.objective(lpec2)*1000))*100
```
The integer restricts nearly 1.87% about the value of return.


```{r}
abc<-cbind.data.frame(Colnames,get.variables(lpec2)*1000,get.variables(lpec3))
abc$pre<-round((log(abc$`get.variables(lpec3)`)-log(abc$`get.variables(lpec2) * 1000`))*100,2)
cbind(abc$Colnames,abc$pre)
```
The percentage of investment quantities change is(%):
 "S1" "-18.19"
 "S2" "21.87" 
 "S3" "-47"   
 "H1" "-18.21"
 "H2" "-29.98"
 "H3" "10.53" 
 "C1" "0"     
 "C2" "0"     
